---
title: "Structure to function Regressions"
author: "Matthew Flamini"
date: "March 21, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(ggplot2)
library(stringr)

```

## Anneal Regression
I was able to get a very good fit using am multiple regression model. High correlation, low p value, and very good "goodness of fit" stats, indicating that the data was not over fit. 

```{r data setup, echo = FALSE}
load("C:/Users/Matt/Google Drive/Education/Rowan/BME/Research/autofibers/21Mar2019.RData")

anneal <- all[all$condition == "anneal",]
anneal$index <- seq(1, dim(anneal)[1],1)
quench <- all[all$condition == "quench",]
quench$index <- seq(1, dim(quench)[1],1)

min.all <- unique.rows(all)
min.anneal <- min.all[min.all$condition == "anneal",]
min.quench <- min.all[min.all$condition == "quench",]
```

```{r Anneal Regressions}
anneal.UTS <- lm(UTS_FTIR ~ wamor_or + wcryst_or + tot_or, data = min.anneal)
summary(anneal.UTS)
model_fit_stats(anneal.UTS)
```

## Quench Regression
I could not get the same model to work with the quench data. However, I got a different model that works quite well, and is also suggested by the data. Here I use a 3rd degree polynomial, but it looks like once we increase our sample size, a second degree will fit nicely. Like before, the model has a high predictive value, and does not seem to be over fit based on both the eye test and the fit stats

```{r Quench Plot, echo = FALSE}
gg <- ggplot(min.quench, aes(x = Perc_Cryst, y = UTS_FTIR))+
  geom_point()+
  geom_smooth(method = lm, formula = y ~ poly(x, 3, raw = TRUE))+
  xlab("Crystallinity")+
  ylab("UTS (GPa)")+
  theme_minimal()
gg
```

```{r Quench Qegressions}
quench.UTS <- lm(UTS_FTIR ~ poly(Perc_Cryst , 3, raw = TRUE), data = min.quench)
summary(quench.UTS)
model_fit_stats(quench.UTS)
```

## PCA of Anneal and Quench
In order to determine whether the Quench and Anneal samples differ in some way, I decided to perform PCA on them to determine if they are really distinct populations of fibers. That is to say, an annealed fiber is different than a quenched fiber. 

```{r PCA, echo = FALSE}
pca.all <- subset(min.all, select = c(Perc_Cryst, amor_or, cryst_or, tot_or))
```

```{r PCA cont., echo = TRUE}
pca.all.df  <- prcomp(pca.all, scale = TRUE, center = TRUE)
```

```{r PCA cont2., echo = FALSE}
pca.all.values <- data.frame(pca.all.df$x, Condition = min.all$condition, temp <- min.all$temp, UTS <- min.all$UTS_FTIR)
pca.all.loadings <- data.frame(Variables = rownames(pca.all.df$rotation), pca.all.df$rotation)

gg <- ggplot(pca.all.values,aes(x=PC1,y=-PC2, color = Condition))+
  geom_segment(data = pca.all.loadings, aes(x = 0, y = 0, xend = (PC1*3),
      yend = (PC2*3)), arrow = arrow(length = unit(1/2, "picas")),
      color = "black", size = 1, alpha = .3) +
  geom_point(aes(size=UTS), alpha = .4)+
  geom_text(aes(label = as.character(temp)), hjust=-.75 ,vjust=1.5, alpha = .8, color = "black")+
  annotate("text", x = (pca.all.loadings$PC1*3.5), y = (pca.all.loadings$PC2*3.5),#label = pca.loadings$Variables)+
           label = c("Crystallinity","Amorphous Or.","Crystal Or.","Total Or."))+ #pca.loadings$Variables)+
  #ggtitle(label = "PC1 vs PC2 of Annealed and Quenched Samples")+
         # subtitle = "PCA computed using Percent Crystallinity, and amorphous, crystal, and total Orientation")+
  scale_size_continuous( range = c(3,12),
             breaks = c(.232, .4 , .6 , .8 , .99),
             labels = c(.2, .4 , .6 , .8 , 1))+
  labs(color = "Condition",
       size = "UTS (GPa)")+
  guides(colour = guide_legend(override.aes = list(size=10)))+
 # xlim(-3.5,2.5)+
  theme_minimal(base_size = 22)

png(filename=paste(getwd(),"/quenchVsAnnealPCA.png", sep = ""),
    type="cairo",
    units="in",
    width=10.5,
    height=8,
    pointsize=12,
    res=1000)

gg
dev.off()

knitr::include_graphics(paste(getwd(),"/quenchVsAnnealPCA.png", sep = ""))
```

## Stress Strain Curves

In order to visualize the changes in strength as a function of temperature, I have arranged the stress strain curves and their derivatives side by side according to the temperature they were treated. 

### Anneal
It seems like the annealled samples got weaker, and then stronger. This indicated more than one factor.

```{r Stress vs Strain Anneal, echo = FALSE}

sequenctial_SS_YManneal(anneal, path = getwd())
knitr::include_graphics(paste(getwd(),"/ymAndssSequentialanneal.png", sep = ""))
```

### Quench
These samples only got stronger. At least until they hit a maximum strength around 68 degrees. 

```{r Stress vs Strain Quench, echo = FALSE}
sequenctial_SS_YMquench(quench, path = getwd())

knitr::include_graphics(paste(getwd(),"/ymAndssSequentialquench.png", sep = ""))
```


## Alignment vs Temp

### *Amorphous*


```{r, Alignment vs Temp, echo = FALSE}
gg <- ggplot(min.all, aes(as.numeric(temp),amor_or))+
  geom_point(aes(color = condition), size = 4)+
  geom_line(aes(color = condition))+
  theme_minimal(base_size = 22)

png(filename=paste(getwd(),"/amor_orVStemp.png", sep = ""),
    type="cairo",
    units="in",
    width=10.5,
    height=8,
    pointsize=12,
    res=1000)

gg
dev.off()

knitr::include_graphics(paste(getwd(),"/amor_orVStemp.png", sep = ""))
```

### *Crystalline*


```{r, Alignment vs Temp (crystal), echo = FALSE}
gg <- ggplot(min.all, aes(as.numeric(temp),cryst_or))+
  geom_point(aes(color = condition), size = 4)+
  geom_line(aes(color = condition))+
  theme_minimal(base_size = 22)

png(filename=paste(getwd(),"/cryst_orVStemp.png", sep = ""),
    type="cairo",
    units="in",
    width=10.5,
    height=8,
    pointsize=12,
    res=1000)

gg
dev.off()

knitr::include_graphics(paste(getwd(),"/cryst_orVStemp.png", sep = ""))
```

## Crystallinity


```{r, Crystallinity, echo = FALSE}
gg <- ggplot(min.all, aes(as.numeric(temp),Perc_Cryst))+
  geom_point(aes(color = condition), size = 4)+
  geom_line(aes(color = condition))+
  theme_minimal(base_size = 22)

png(filename=paste(getwd(),"/Perc_CrystVStemp.png", sep = ""),
    type="cairo",
    units="in",
    width=10.5,
    height=8,
    pointsize=12,
    res=1000)

gg
dev.off()

knitr::include_graphics(paste(getwd(),"/Perc_CrystVStemp.png", sep = ""))
```


## Young's Modulus


```{r, Young's Modulus, echo = FALSE}
gg <- ggplot(min.all, aes(as.numeric(temp),ymMax))+
  geom_point(aes(color = condition), size = 4)+
  geom_line(aes(color = condition))+
  theme_minimal(base_size = 22)

png(filename=paste(getwd(),"/ymVStemp.png", sep = ""),
    type="cairo",
    units="in",
    width=10.5,
    height=8,
    pointsize=12,
    res=1000)

gg
dev.off()

knitr::include_graphics(paste(getwd(),"/ymVStemp.png", sep = ""))
```
